Light Transport Techniques for Tensor Field Visualization

### 2019-08-05 beamer2thesis/dummy.tex
update

%\frame[plain]{\titlepage}

\frame{
\frametitle{{Propagation Scheme - Template}}
\begin{columns}
\begin{column}{.6\textwidth}
To interpret eigensystems of tensors as conductivity property for light transport, we will need a propagation scheme:\bigskip
\begin{itemize}
	\item using light propagation volumes (LPV) similar to Dachsbacher et al. (cf. Fig.)\bigskip
	\item exchanging itensities between neighboring cells: $\Phi_{t} = \int I(\omega)\mathop{d\omega}$\\
	{\small with $\Phi_{t}$: radiant flux, $I(\omega)$: radiant intensity}
\end{itemize}

\end{column}
\begin{column}{.4\textwidth}
\begin{figure}[t]
\centering
\begin{minipage}{0.79\textwidth}
\centering
\includegraphics[width=0.7\textwidth]{LPV.pdf}
\includegraphics[width=0.9\textwidth]{LPV2.pdf}
\caption*{Light Propagation Volumes}
\end{minipage}
\begin{minipage}{0.15\textwidth}
\source{\textit{A. Kaplanyan and C. Dachsbacher, ''Cascaded light}} 
\hspace{-3pt} {\tiny \raisebox{-0.75in}{\rotatebox[origin=t]{90}{propagation volumes for realtime indirect illumination"}}}
\end{minipage}
\end{figure}

\end{column}
\end{columns}
} % END OF FRAME

>>>>

\frame[plain]{\titlepage}
\frame{
\frametitle{{Light Transport Gradient - Scheme}}
\begin{figure}[t]
\centering
  \begin{minipage}{0.6\textwidth}
  \centering
	\includegraphics[height=0.7\textwidth]{skizze/addins/grids_one_base_edit.pdf}
	\caption*{Light Transport Gradient - Domain of Light Distributions}
	\end{minipage}
\end{figure}

} % END OF FRAME

\frame{
\frametitle{{Light Transport Gradient - Scheme}}
\begin{figure}[t]
\centering
  \begin{minipage}{0.6\textwidth}
  \centering
	\includegraphics[height=0.7\textwidth]{skizze/addins/grids_one_edit.pdf}
	\caption*{Light Transport Gradient - Domain of Light Distributions}
	\end{minipage}
\end{figure}

} % END OF FRAME

\frame{
\frametitle{{Light Transport Gradient - Scheme}}
\begin{figure}[t]
\centering
  \begin{minipage}{0.5\textwidth}
  \centering
	\includegraphics[height=0.85\textwidth]{skizze/addins/grid_two_base.pdf}
	\caption*{Light Transport Gradient - Neighborhood}
	\end{minipage}
\end{figure}

} % END OF FRAME
\frame{
\frametitle{{Light Transport Gradient - Scheme}}
\begin{figure}[t]
\centering
  \begin{minipage}{0.5\textwidth}
  \centering
	\includegraphics[height=0.85\textwidth]{skizze/addins/grids_two_edit.pdf}
	\caption*{Light Transport Gradient - Neighborhood}
	\end{minipage}
\end{figure}

} % END OF FRAME
